### 2014-09-03 tex/proofs.tex
Committing changes before merge.

%proof for field write
\begin{lemma}[Exactness of Field Write Rule]
\label{lem:write}
If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \eta\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{k}\ \emptyset)$.

\end{lemma}
\begin{proof}
By Lemma~\ref{lem:init} we know that if $s_s$ is exact, then the intermediate state $s_x$ such that $s_s \rightarrow_S^* s_x$ is also exact. Thus, for $s_s$ and any state  $s_i$ such that $s_i \sqsubset s_s$ we will assume, without loss of generality, that all relevant fields have been initialized.

First, we show that every state in the feasible set is represented by $s_s^\prime$. Take some lazy state $s_i$ such that $s_i \sqsubset s_s$. Observe that the field write rule places every possible target value into the reference stored at the target location. Thus, whatever the write value was for $s_i^\prime$ was, it was written to the target field, meaning $s_i^\prime$ is represented by $s_s^\prime$.

>>>>

%proof for field write
\begin{lemma}[Exactness of Field Write Rule]
\label{lem:write}
If symbolic state $s_s =  \lp \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta\ \cfgnt{r}\ \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, and if $s_s \rightarrow_s s_s^\prime$ for some state $s_s^\prime$, then $s_s^\prime$ is equal to $ \lp \cfgnt{L}_{s^\prime}\ \cfgnt{R}_{s^\prime}\ \phi_{s^\prime}\ \eta\ \cfgnt{k}\rp$ and is exact with respect to $s_0$ and $\pi_n \ (\eta\ \cfgnt{k}\ \emptyset)$:
$$s_\ell^\prime \sqsubset s_s^\prime \Leftrightarrow s_\ell^\prime \in \mathbb{FS}(\rightarrow_\ell, s_0, \pi_n (\eta\ \cfgnt{k}\ \emptyset) ) $$

\end{lemma}
\begin{proof}
Begin by assuming the conditions from Lemma~\ref{lem:write}.

The first step is to show that $s_s^\prime$ is complete with respect to the feasible set. Take any lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$, and find state $s_\ell^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$. Let $l_\ell$ be the location such that $\{(\phi\ l_\ell )\} = \cfgnt{L}_\ell(\cfgnt{r}_x) $ for some $\phi$. To show that $s_\ell^\prime \sqsubset s_s^\prime$, we need to demonstrate that there exists a function $h^\prime$ such that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, and that $\mathbb{S}(\phi_{s^\prime} \wedge \mathbb{HC}(s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime) )$. Since $s_h \sqsubset s_s$, we know that there exists a function $h$ such that $s_\ell \rightharpoonup_{h} s_s$. Let $h^\prime = h$.

To see that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$, we must consider how $s_s^\prime$ is constructed. Let $l_\alpha$ and $l_\beta$ be arbitrary locations in $\cfgnt{L}_{\ell^\prime}^\rightarrow$ such that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f ))$, let $\theta = \cfgnt{L}_s(\cfgnt{R}_s(h(l_\ell),f))$, and let $\theta^\prime =   \cfgnt{L}_s^\prime(\cfgnt{R}_s^\prime(h(l_\ell),f))$. If $l_\beta \neq l_\ell$, then either $\theta = \theta^\prime$ or $\theta \neq \theta^\prime$ . In the first case, we are guaranteed that the homomorphism works by default. Otherwise, if $\theta \neq \theta^\prime$.  We can see from the construction of the set $X$ in the summary Field Write rule that any feasible location in the set $\theta$ must also be in the set $\theta^\prime$. Since $s_\ell \sqsubset s_s$, we know that $h(l_\alpha)$ is in $\theta$, and is likewise in $\theta^\prime$. We have now established that in either case:
 $$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
On the other hand, if $l_\beta = l_\ell$, then we know that $\{(\phi_a\ \cfgnt{l}_\alpha)\} = \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\ell,f ))$. From the lazy field rule, we can use the fact that $ $ surmise that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell}( )$, and since $s_\ell \sqsubset s_s$, we know $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s}(\cfgnt{r}_x)$ for some constraint $phi_b$. Using this fact, we can apply the summary Field Write rule to infer that $l_\alpha$ must be one of the locations in $\theta^\prime$, and therefore $(\phi_b\ h(\cfgnt{l}_\alpha)) \in \cfgnt{L}_{s^\prime}(adfa)$

Thus, for arbitrary $l_\alpha$ and $l_\beta$:
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\ell^\prime}(\cfgnt{R}_{\ell^\prime}(\cfgnt{l}_\beta,f )) \Rightarrow (\phi_b\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (h(\cfgnt{l}_\beta),f ))$$
Therefore, we have shown that $s_\ell^\prime \rightharpoonup_{h^\prime} s_s^\prime$.

Observe that the field write rule places every possible target value into the reference stored at the target location. Thus, whatever the write value was for $s_i^\prime$ was, it was written to the target field, meaning $s_i^\prime$ is represented by $s_s^\prime$.
